Is high social class always beneficial for survival? Long-term perspectives

### 2017-07-30 article.Rmd
add word_output

---
title: Is high social class always beneficial for survival? Long-term perspectives
  of social inequality in mortality among adults and elderly in Northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: "24 July 2017"
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
link-citations: yes
bibliography: mybib.bib
biblio-style: apalike
---

>>>>

---
title: Is high social class always beneficial for survival? Long-term perspectives
  of social inequality in mortality among adults and elderly in Northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: '`r Sys.Date()`'
output:
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
link-citations: yes
bibliography: mybib.bib
biblio-style: apalike
---
